### 2016-09-25 results.tex
commenting on Jon's meta-theorem

\def\bool{\{0,1\}}

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \bool^n \times \bool^{\ell_{in}} \rightarrow \bool^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S$ and outputs distinct values $x_1, \ldots, x_t \in \bool^{\ell_{in}}$,
where $t$ depends only on~$|S|$.
\item $\Rep_2$ takes as input $|S|$ and $y_1, \ldots, y_t \in \bool^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
\begin{enumerate}
\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
\item $k \getsr \bool^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
\end{enumerate}
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$.
\end{definition}
\jnote{Not sure how general to make the above. Need to verify that it is general enough
to prove security of all the constructions we care about.}

We next show that any canonical data structure in which $F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

\begin{theorem}
Let $\Pi=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom function, then $\Pi$
is semantically secure with respect to leakage function ${\sf leak}(S) = |S|$.
\end{theorem}
\begin{proof}
We define the following simulator $\Sim$: on input $n$, define $S^*=\{e_1, \ldots, e_n\}$
(for distinct elements $e_1, \ldots, e_n$). Then compute
\begin{enumerate}
\item $x_1, \ldots, x_t \getsr \Rep_1(S^*)$,
\item $k \getsr \bool^n$,
\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$,
\end{enumerate}
and output $\pubaux$.

@@

For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
and define distribution $\mbox{{\sf Ideal}}_S$ as
\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
like this in the concrete setting.}
To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
the following experiment:
\begin{enumerate}
\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
\item $k \getsr \bool^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
\item Return $\pubaux$.
\end{enumerate}

Now, consider a hybrid distribution $\hyb_S$ computed as follows:
\begin{enumerate}
\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bool^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $\pubaux$.
\end{enumerate}
It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.

Next, consider the following distribution $\hyb'_S$:
\begin{enumerate}
\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
\item $x_1, \ldots, x_{t^*} \getsr \Rep_1(S^*)$.
\item $y_1, \ldots, y_{t^*} \leftarrow \bool^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
\item Return $\pubaux$.
\end{enumerate}
We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
(in $\hyb'_S$) by definition
of what it means to be canonical.

@@

\jnote{Organize by scheme, not by security notions.}

@@

\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Should follow from Jon's general result(?)}

>>>>

\def\bits{\{0,1\}}

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \calK$.
\item $\pubaux \getsr \Rep_2(n, F_K(s_1), \ldots,F_K(s_t))$. 
\end{enumerate}
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
\jnote{Not sure how general to make the above. Need to verify that it is general enough
to prove security of all the constructions we care about.}
\tsnote{Would be good to give an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. It does not cover
  linear-PRF or Neidermayer. }
We next show that any canonical data structure in which $F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

\begin{theorem}
Let $\Pi=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
function \tsnote{overloading~$t$}, then $\Pi$ is semantically secure
with respect to leakage function ${\sf leak}(S) = |S|$.
\tsnote{We have a mixture of styles of theorem statements, resource-parameterized statements vs.\ ``verbose'' concrete statements.  We
  need to make things uniform.}
\end{theorem}
\begin{proof}
We define the following simulator $\Sim$: on input $n$, define $S^*=\{e_1, \ldots, e_n\}$
(for distinct elements $e_1, \ldots, e_n$). Then compute
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S^*)$,
\item $K \getsr \calK$,
\item $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$,
\end{enumerate}
and output $\pubaux$.

@@

For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
and define distribution $\mbox{{\sf Ideal}}_S$ as
\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
like this in the concrete setting.}\tsnote{I think you just follow the
sketch that I typeset for the Domain-Separated PRF scheme. (I'll embed
notes below, too.) The bound will be exactly what is there, shoudl be able to just cut-and-paste,
basically.  All that's needed, I think, is to do resource accounting
for $\Sim$ and the PRF-adversary~$B$.}
To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
the following experiment: \tsnote{I'd call this ``Game $G0$''...}
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \bits^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
\item Return $\pubaux$.
\end{enumerate}

Now, consider a hybrid distribution $\hyb_S$ computed as follows:
\tsnote{...and this ``Game $G1$''...}
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $\pubaux$.
\end{enumerate}
It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
\tsnote{...and then it's clear that the difference between the
  probability of $G0 \outputs 1$ and $G1 \outputs 1$ is exactly the
  PRF advantage of~$B$, who simply uses it's oracle to simulate calls
  to $F_K$ prior to running $\Rep_2$...}
Next, consider the following distribution $\hyb'_S$:
\begin{enumerate}
\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
\item $s_1, \ldots, s_{t^*} \getsr \Rep_1(S^*)$.
\item $y_1, \ldots, y_{t^*} \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
\item Return $\pubaux$.
\end{enumerate}
We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
(in $\hyb'_S$) by definition
of what it means to be canonical.
\tsnote{...and it is clear that the distriubtion of everything is the
  same as in Game $G1$, so we are done. }

@@

%\jnote{Organize by scheme, not by security notions.}

@@

\todo{Privacy theorem for the ``plain'' linear-PRF scheme. Does not
  follow from Jon's general theorem.}
